### 2012-06-26 trunk/ijcis-pos-model/sources/temporalModel.tex
final changes

\begin{definition}
\emph{Generalized fuzzy temporal relation.}
\label{def:fuzzy-temporal-relation}
Consider the elements in definition \ref{def:valid-time-relation}. Some of the elements will be extended for the fuzzy case.

\begin{itemize}
 \item A set of non-temporal fuzzy  or crisp attributes.
	\begin{equation}
	\label{eq:fuzzy-attribute-set}
	A = \left \lbrace A_1, A_2, \ldots, A_n \right \rbrace
	\end{equation}
      The domain for each attribute $A_1, \ldots, A_n$ is $D_1, \ldots, D_n$ respectively. 
\item The primary key $A_K$ is a subset of $A$.
      \begin{equation}
       \label{eq:fuzzy-primary-key-a}
      A_K \subset A
      \end{equation}
A formal definition of primary key for fuzzy relational databases will be given later in Definition \ref{def:generalized-primary-key}.
\item A set of two attributes; $S$  and $E$ the attributes for the starting and ending ill-known points respectively. $I$ is a possibilistic validity period \emph{PVP} as explained in Section \ref{subsec:ill-known-interval}.
\begin{equation}
 \label{eq:fuzzy-attribute-time-interval}
I = \left \lbrace S, E \right \rbrace
\end{equation}
\item An attribute called version identifier, $V_{ID}$. This attribute is a counter for each different version of the entities. 
% \begin{equation}
%  \label{eq:fuzzy-version-identifier}
% V_{ID} \subset \N
% \end{equation}

@@

\item Let $t$ be a tuple in the instance $r$; $t \in r$:
      \begin{itemize}
      \item We will note the values for the starting and the ending  points,$s$ and $e$  respectively. The value for the time interval is given by $i$.
      \begin{align}
       \label{eq:fuzzy-starting-point}
      s = t\left[S \right]\\
      e = t\left[E \right]\\
      i = \left(s, e\right)
      \end{align}

      \item Let $A_k \subset A$ be the set of the non-temporal attributes that are part of the primary key (equation \eqref{eq:fuzzy-primary-key-a}). Then, $a_k$ denotes the values for the non-temporal attributes of the primary key.
	    \begin{equation}
	     \label{eq:fuzzy-pk-attribute} 
	      a_k = t\left[A_K \right]
	    \end{equation}

    \item Let $K_{GT}$ be the primary key for the valid-time relation as given in equation \eqref{eq:fuzzy-valid-time-temporal-pk}. Then, $k$ denotes the values for the attributes in the primary key.
	  \begin{equation}
	   \label{eq:fuzzy-value-pk}
	  k = t\left[K_{GT} \right]
	  \end{equation}

      \end{itemize}
\item $Vt$ is the set with all the versions for a given tuple $t$.

\begin{equation}
 \label{eq:fuzzy-all-the-versions}
Vt = r\left(t\left[A_K\right] \right)
\end{equation}
If a tuple $t$ contains more than one version, the result of $Vt$ is a set. We will use the index $k$ to address the elements of the set. E.g. $Vt = \left \lbrace t_1, t_2, \ldots, t_n \right \rbrace$. Then $t_k , k \in \left \lbrace 1, \ldots, n \right \rbrace$ is an element of $Vt$.
\end{itemize}
%\end{definition}

@@

\begin{align}
\label{eq:insert-fuzzy-temporal}
\INS \left(r, t\right) &=\\
\INS \left(r, t\right) =\\
\begin{cases}
\nonumber
r \cup \lbrace t \rbrace
& \mbox{ if }  t \not \in r \mbox{ or }\\
\nonumber & \forall t_k \in Vt,  \left(i \mbox{ Overlaps } i_k\right) < 1\\
% 
% R \cup \left(A, I \right) & \mbox{ if }  (A, I ) \not \in R  \mbox{ or } \\
%  &   \left(A, J\right) \in R \mbox{ and } \lnot \left(I \mbox{ Overlaps } J\right) \\
\mbox{modify(r, t)} & \mbox{ otherwise }    %\mbox{ if } \exists J \left(A,J\right) \in R \wedge \mbox{Current(A,J)} \\ 
%R, &   
\end{cases} 	
\end{align}
\subsubsection{\label{subsubsec:delete-fuzzy-temporal}Delete}
The delete operation logically removes an entity which is valid in the instance $r$ of the relation $R_{FTG}$.

@@

\begin{align}
\label{eq:delete-fuzzy-temporal}
\\DEL \left(r, t\right) =
\begin{cases}
\nonumber
r - Vt
\end{cases} 	
\end{align}

>>>>

\begin{definition}
\emph{Generalized fuzzy temporal relation.}
\label{def:fuzzy-temporal-relation}
Consider the elements in definition \ref{def:valid-time-relation}. Some of them will be extended for the fuzzy case.

\begin{itemize}
%  \item A set of non-temporal fuzzy  or crisp attributes.
% 	\begin{equation}
% 	\label{eq:fuzzy-attribute-set}
% 	A = \left \lbrace A_1, A_2, \ldots, A_n \right \rbrace
% 	\end{equation}
%       The domain for each attribute $A_1, \ldots, A_n$ is $D_1, \ldots, D_n$ respectively. 
% \item The primary key $A_K$ is a subset of $A$.
%       \begin{equation}
%        \label{eq:fuzzy-primary-key-a}
%       A_K \subset A
%       \end{equation}
% A formal definition of primary key for fuzzy relational databases will be given later in Definition \ref{def:generalized-primary-key}.
% \item A set of two attributes; $S$  and $E$ the attributes for the starting and ending ill-known points respectively. $I$ is a possibilistic validity period \emph{PVP} as explained in Section \ref{subsec:ill-known-interval}.
% \begin{equation}
%  \label{eq:fuzzy-attribute-time-interval}
% I = \left \lbrace S, E \right \rbrace
% \end{equation}
\item An attribute called version identifier, $V_{ID}$, will be added to the schema. This attribute is a counter for each different version of the entities. 
% \begin{equation}
%  \label{eq:fuzzy-version-identifier}
% V_{ID} \subset \N
% \end{equation}

@@

% \item Let $t$ be a tuple in the instance $r$; $t \in r$:
%       \begin{itemize}
%       \item We will note the values for the starting and the ending  points,$s$ and $e$  respectively. The value for the time interval is given by $i$.
%       \begin{align}
%        \label{eq:fuzzy-starting-point}
%       s = t\left[S \right]\\
%       e = t\left[E \right]\\
%       i = \left(s, e\right)
%       \end{align}
% 
% 
%       \item Let $A_k \subset A$ be the set of the non-temporal attributes that are part of the primary key (equation \eqref{eq:fuzzy-primary-key-a}). Then, $a_k$ denotes the values for the non-temporal attributes of the primary key.
% 	    \begin{equation}
% 	     \label{eq:fuzzy-pk-attribute} 
% 	      a_k = t\left[A_K \right]
% 	    \end{equation}
% 
    \item Let $K_{GT}$ be the primary key for the valid-time relation as given in equation \eqref{eq:fuzzy-valid-time-temporal-pk}. Then, $k$ denotes the values for the attributes in the primary key.
	  \begin{equation}
	   \label{eq:fuzzy-value-pk}
	  k = t\left[K_{GT} \right]
	  \end{equation}
% 
% 
%       \end{itemize}
% \item $Vt$ is the set with all the versions for a given tuple $t$.
% 
% \begin{equation}
%  \label{eq:fuzzy-all-the-versions}
% Vt = r\left(t\left[A_K\right] \right)
% \end{equation}
% If a tuple $t$ contains more than one version, the result of $Vt$ is a set. We will use the index $k$ to address the elements of the set. E.g. $Vt = \left \lbrace t_1, t_2, \ldots, t_n \right \rbrace$. Then $t_k , k \in \left \lbrace 1, \ldots, n \right \rbrace$ is an element of $Vt$.
\end{itemize}
%\end{definition}

@@

\begin{align}
\label{eq:insert-fuzzy-temporal}
\INS \left(r, t\right) &=\\
\begin{cases}
\nonumber
r \cup \lbrace t \rbrace
& \mbox{ if }  t \not \in r \mbox{ or }\\
\nonumber & \forall t_k \in Vt,  \left(i \mbox{ Overlaps } i_k\right) < 1\\
% 
% R \cup \left(A, I \right) & \mbox{ if }  (A, I ) \not \in R  \mbox{ or } \\
%  &   \left(A, J\right) \in R \mbox{ and } \lnot \left(I \mbox{ Overlaps } J\right) \\
\mbox{modify(r, t)} & \mbox{ otherwise }    %\mbox{ if } \exists J \left(A,J\right) \in R \wedge \mbox{Current(A,J)} \\ 
%R, &   
\end{cases} 	
\end{align}
\subsubsection{\label{subsubsec:delete-fuzzy-temporal}Delete}
The delete operation logically removes an entity which is valid in the instance $r$ of the relation $R_{FTG}$.

@@

\begin{align}
\label{eq:delete-fuzzy-temporal}
\DEL \left(r, t\right) =
\begin{cases}
\nonumber
r - Vt
\end{cases} 	
\end{align}
